---
title             : "Intentional Self Regulation is Not Sufficient: The argument for understanding risk appraisal"
shorttitle        : "Understanding Goal Directed Action in Context"

author: 
  - name          : "Andrew G. Farina"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Eliot-Pearson Department of Child Study and Human Development, Tufts University, Medford, MA 02155"
    email         : "Andrew.Farina@tufts.edu"

affiliation:
  - id            : "1"
    institution   : "Tufts University"

authornote: |
  Andrew G. Farina, Eliot-Pearson Department of Child Study and Human Development, Tufts University. This research was supported by the John Templeton Foundation.  


abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : r-references.bib

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_docx
---

```{r setup, include = FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, papaja, academicWriteR)

select <- dplyr::select
```

When individuals make decisions that will impact their long term 

Describe the context first (risk taking/goal setting in leadership)
Decision Making? Risk taking in decisions? - interesting research in this field--
Define Risk, Risk Taking, Risk Propensity, and Risk Appraisal.

do decisions become "better"/ more informed with age and experience?  If so, then  how does 'risk' play into this?

# Risk Taking during Adolescence

Discuss the papers that question whether adolesence take more risks...instead it highlights the difference in risk appraisal.

Why do adolescence take risks?

## Dual Model
Dual Model to explain it… (sensation seeking with absense of self regulation capacities)
Describe reductionist and Deficit Model
Insufficient to describe the ‘development’ through constraints/ timing/ person…must bring in context

# Dynamic Systems Approach

## Action Theory

## Intentional Self Regulation

## SOC- The model of selection, optimizaiton, and compensation @ baltes 1990, @Frieund 2002

## TENFLEX- dual-process model of assimilative and accommodative coping @Brandstadter, 1989

## Primary/Secondary Control- motiviational theory of lifespan development @heckhausen 2010, 1993

## Describe commonalities of these three approaches from @haase 2013

## Development of Self Regulation Capacities (4H study and subsequent studies)

## Development of Prudent Risk Taking using Dynamic Systems Approach

How could we use this to describe the development of risk taking during adolescence?
Challenge/ Scaffolding/ confidence gaining- repeat

# New model of Self Regulation
Propose new model of Intentional Self Regulation that includes risk taking as a central theme?

# Implications
Where do we go from here??

$\leftrightarrow$
$\longleftrightarrow$



\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
